Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Reviewed a bit of Annika's text

Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
  \caption{%
    \textbf{Two possible setups for a SSC microscope.}
    \textbf{a:} Diagram of the combined setup with a xyz sample scan.
    \textbf{b:} Diagram of the combined setup with a xy sample scan and a z probe and objective scan. 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sscm_setup}
\end{figure}

The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
SICM probe at a fixed position. The focus of the confocal FM objective is adjusted to the tip of SICM 
probe for vertical alignment. To achieve lateral alignment of probe and pinhole mechanical 
micromanipulators are used. Once the setup is aligned, the sample stage moves the sample in all three 
dimensions (xyz) for imaging.

The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
alteration: the sample stage only moves in xy dimensions while objective and probe have been equipped 
with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
all three dimensions, it is only moved in x and y directions, while probe and objective, controlled by
the same software, simultaneously move in z direction.

According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
of the 3D piezo-actuator acted as a limiting factor. Additionally, usage of three piezo-elements on the
same platform lead to cross-talk and consequentially artefacts in the SICM data.

>>>>

Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a
combination of SICM and scanning confocal microscopy (SCM) which enables
simultaneous SICM and FM imaging of the surface of the same sample. In SSCM,
the fluorescence data for each pixel is recorded at the position determined by
SICM for that pixel. Up to now, two slightly different setups have been proposed
(Fig.~\ref{fig:sscm_setup}) \cite{Gorelik2002,Shevchuk2013}.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}

  \caption{%
    \textbf{Two setups for a SSC microscope.}
    \textbf{a:} Diagram of the combined setup with an $x,y,z$ sample scanner.
    \textbf{b:} Diagram of the combined setup with a $x,y$ sample scanner and
    a $z$-probe and objective scanner. 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sscm_setup}
\end{figure}

In both setups, an SICM is mounted onto an inverted confocal microscope and
before simultaneous recording, the focus of the confocal FM objective is
aligned with the tip of the SICM probe via micrometer screws and the confocal
microscope's focusing mechanics. The
difference between the two setups is the way how the SICM pipette, the
confocal focus and the sample are positioned with respect to each other during
imaging. The
first setup (Fig.~\ref{fig:sscm_setup}a) keeps the 
SICM probe at a fixed position and scanning is performed by the sample
stage which positions the sample in all three dimensions.

In contrast, the second setup (Fig.~\ref{fig:sscm_setup}b) uses the sample
stage to position the sample in $x$- and $y$-direction only while objective
and probe are positioned by additional piezo elements in $z$-direction. Thus,
when the surface is detected by the SICM pipette, subsequently the position of
the confocal spot has to be adjusted by the objective positioning piezo.

Both setups do not allow to use the controlling software of the confocal
microscope since the fluorescence data has to be recorded after the SICM
pipette has detected the surface. Thus, the SICM controlling soft- and
hardware had to be extended to at least allow reading from the detectors of
the confocal microscope.

Switching from full stage scanning to $z$-movement of the pipette allows for
faster scan rates as the resonant frequency of the 3D piezo-actuator acted as
a limiting factor. Additionally, usage of three piezo-elements on the same
platform led to cross-talk and consequentially artefacts in the SICM data
\cite{Shevchuk2013}.

% Bis hier überarbeitet.
